---
output: 
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    latex_engine: xelatex
    number_sections: yes
    template: ./svm-latex-syllabus.tex
  geometry: margin=1in
title: "POLI 618: Techniques of Empirical Research"
author: Professor Aaron Erlich
date: "Autumn 2017"
email: "aaron.erlich@mcgill.ca"
phone: 514-398-4756
officehours: W 4-5 F 10-11 (drop-in)
office: "3610 McTavish, Room 26-4"
classroom: "MUSIC A-412"
classhours: "W,F 8:55 AM - 9:55 AM"


TA:
  - {name: "Aengus Bridgman", 
     email: "aengus.bridgman@mail.mcgill.ca", 
     office: "TBD",
     officehours: "TBD",
     conferencehours: "TBD"}

fontfamily: mathpazo
fontsize: 11pt
header-includes:
   - \linespread{1.05}
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=FALSE, dev='pdf')
mon <- as.Date("2016-09-04")
# fri <- as.Date("2016-01-08")

#DEFINE COURSE DATES
#quiz1 <- as.Date("2016-10-11")
#quiz2 <- as.Date("2016-11-10")

paperCheckIn <- as.Date("2017-10-23")
FinalPaper <- as.Date("2017-10-09")
Poster <- as.Date("2016-12-01")
lastClassDay <- as.Date("2017-12-01")
endExamDay <- as.Date("2016-12-21")

formatCourseDate <- function(date) {
  date <- format(date, format="%A, %b %d")
  return(date)
}

advdate <- function(obj, adv) {
 tmon <- obj + 7*(adv-1)
 tfri <- obj + 4 + 7*(adv-1)
 tmon <- format(tmon, format="%m/%d")
 tfri <- format(tfri, format="%m/%d")
 zadv <- sprintf("%02d", adv)
 tmp <- paste("Week ",zadv,sep='',", ", tmon," - ",tfri)
 return(tmp)
}

library(RefManageR)
library(knitcitations)
library(rcrossref)
#FIX to source bib fro class
bib <- ReadBib("syllabus_618.bib")
myopts <- BibOptions(bib.style = "authoryear", style="latex", first.inits=FALSE, max.names = 20)

```

# Course Description
This course is designed to introduce graduate students to the new and exciting world of data driven political analysis. The course employs examples from across political science sub-disciplines and is generally relevant to all social science research. The course is divided into lectures and labs.

## Who this course is for?

* This is your first semester-long course on graduate quantitative methods course for data analysis. 

* You are willing to spend time considerable outside of the classroom to learn the course materials, as data analysis is a skill learned by doing.

# Course Objectives

1. Learn the basic tools of empirical research in political science.

2. Obtain skills in  R, a highly powerful and FREE programming language used extensively by academics in political science across the world, as well as the open source and data science community.

3. Understand scientific replicability.

4. Gain real world skills that will help you obtain jobs in careers of the future. 

#Textbooks
Given people's various backgrounds, we will have three required and several optional textbooks in addition to the assigned articles. The Bailey book is a great book and very applied. Everyone should read it. For those of you seriously interested in pursuing quantitative analysis, you should then read the Fox book on top of the Bailey book. Unless otherwise cleared with me, everyone is required to do the math review problems assigned from the Moore book. The Grolemund and Wickham book is a great tool (that is online and free) and can often be used in lieu of videos or to help with coding. 

```{r, echo = FALSE, results="asis"} 
bib[author = "Bailey"]
cat("\n")
bib[author = "Moore"]
cat("\n")
bib[author = "Grolemund"]
``` 

#Recommended
```{r, echo = FALSE, results = "asis"}
bib[author = "Fox"]
```

#R and R-Studio
R is a FREE open source programming language uses by data scientists and statisticians across the world. We will be using a FREE graphical user interface (GUI) called **RStudio** that makes learning R easier. While the learning curve in R is steeper than expensive programs, there is much more you can do with it!

There are many free online tutorial for downloading and installing R and RStudio. R will also be available on the conference computers.

# Evaluation Policy
A description of the means of evaluation to be used in the course:

There are 1000 points available in the class. Therefore, for each 10% of the grade, 100 points are allotted.

- **10%**. *Attendance and participation.*

- **40%**. *Problem sets*. A quarter of this grade will be from peer-reviewing each others' assignments on *GitHub*.

- **10%** *Final Presentation*. In class presentation of research.

- **40%** *Final Paper*. A paper --- likely  a replication paper or part of your dissertation or MA Thesis. 
 

##Re-Grading
Students who wish to contest a grade for an assignment or exam must do so in writing (by email, sent to me) providing the reasoning behind their challenge to the grade received within two weeks of the day on which the assignments are returned. I will re-evaluate the paper, but also reserve the right to **raise or lower the grade**. Please also see (http://www.mcgill.ca/politicalscience/files/politicalscience/assessment_and_re-read_policy_final.pdf).


```{r, include=FALSE}
# options(scipen=999)
# Attend <- read.csv("~/Dropbox/teaching/attendance-grades-relationship.csv")
# Attend$rgrade <- round(Attend$grade, 0)
# Attend$perattend <- (Attend$attendance/Attend$max)*100
# Attend <- subset(Attend, !is.na(rgrade))
# Attend$name <- as.numeric(Attend$name)
# Attend$id <- as.numeric(Attend$id)
# Attend$term <- as.numeric(Attend$term)
# Attend$class <- as.numeric(as.factor(Attend$class))
# M1 <- lm(rgrade ~ perattend, Attend)
# M2 <- lm(rgrade ~ perattend, data=subset(Attend, perattend >= 75))
# library(broom)
# 
# M1df <- tidy(M1)
# M2df <- tidy(M2)
# library(ggplot2)
# library(kfigr)
```

#Assignment Submission

Problem sets must be submitted via *GitHub*. You must use a variant \texttt{.Rmd} otherwise known as \texttt{rmarkdown} files that is GitHub compatible to complete your homework. Do not submit your homework using Microsft Word or any other document editor. It will not be graded. Part of your homework grade will be peer-reviewing your colleagues' homework assignments via the course *GitHub*. There will be approximately 5 problem sets. I reserve the right to lower the number of problem sets if needed. In principle, these assignments will be due every 2 weeks starting week 2 for the proceeding 12 weeks of the term. Collaboration is part of learning how to code. I encourage you to collaborate! But you do not learn how to do statistical programming if you DO NOT write your own code. Please feel free to collaborate with colleagues, but please DO NOT copy each others' code verbatim. You must also write your own interpretations of the results.     

##Interim Data Set and Check-in
All students must submit a one page write up of the data set they are going to use and the research question they are going to ask by `r formatCourseDate(paperCheckIn)`. This should be a one page write up in \texttt{rmarkdown} explaining the data set/s which you are going to use and the question you will ask. You should also highlight your outcome variable. Submission will be via *MyCourses*.

## Presentation
Each individual will present their work in class to the rest of the course. All presentations must be completed in .Rpres, revealjs_presentation, or Beamer (LaTeX).

## Paper
All students will submit a final paper that is of article length. This will be done via *MyCourses*. This can be *either* a replication paper with an extension of the original paper *or* a new paper. It is highly recommend you do a replication. Please come talk me as early in the term as possible if you want to write an original paper. An original paper must contain 1) a clear theory proposing a relationship between explanatory variable(s) on an outcome variable; 2) use of linear regression (or some other model cleared with professor); 3) a clear discussion of both findings and limitations of the paper. Students may use a chapter of their master or Ph.D. thesis as a research paper. The paper is due by the end of the exam period `r formatCourseDate(endExamDay)`. 

# Class Discussion List and E-mail Policy
I have set up a class discussion list on *MyCourses*. I encourage you to use this mailing list to ask questions you may have. *NEVER* post your code or specific homework questions on the course list server. Please post general questions! If you post homework code on the website, it will be taken down and your grade may be lowered. 

# Make-Up Work Policy
If you are absent for documented emergency medical or family reasons, an alternative homework submission date will be arranged. The alternative arrangement is only open to those who can provide a valid medical/family reason for missing the quizzes. If you cannot provide a valid reason for your absence, you will receive 0 points for the missed quiz or homework submission. 

Students who need to miss a class due to a religious holiday should notify me at least fourteen
days prior to the holiday. If you must miss a class, an examination, a work assignment, or a
project in order to observe a religious holy day, you will be given an opportunity to complete the missed work within a reasonable time after the absence.


#Technology Policy
## Recording Policy
- No audio or video recording of any kind is allowed in class without the explicit permission of the
instructor.
- Mobile Computing devices are not to be used for voice communication without the explicit permission of the
instructor. 

# Academic Integrity
##Course Policy on Computer Code
As discussed in the problems set section, verbatim copying other people's computer code constitutes plagiarism. Moreover, data programming is learned through trial and error. **Please do not under any circumstances copy another students code.**  You may of course collaborate with colleagues, but please write your own code! If you are found to have plagiarized, you may be referred to the appropriate Dean. The instructors reserve the right to use software to compare the code that has been written by different students. 

## McGill Policy
"McGill University values academic integrity. Therefore, all students must understand the meaning and consequences of cheating, plagiarism and other academic offences under the Code of Student Conduct and Disciplinary Procedures” (see [www.mcgill.ca/students/srr/honest/](www.mcgill.ca/students/srr/honest/) for more information). 


#Other Policies
##Language of Submission:
In accord with McGill University’s Charter of Students’ Rights, students in this course have the right to submit in English or in French any written work that is to be graded. 

## Disabilities Policy
As the instructor of this course I endeavor to provide an inclusive learning environment. However, if you experience barriers to learning in this course, do not hesitate to discuss them with me and the Office for Students with Disabilities, 514-398-6009.

##End of Course Evaluations
End-of-course evaluations are one of the ways that McGill works towards maintaining and improving the quality of courses and the student’s learning experience. You will be notified by e-mail when the evaluations are available. Please note that a minimum number of responses must be received for results to be available to students.
\newpage

# Class Schedule

#### `r advdate(mon, 1)`: Introduction, Prediction and Causation, Intro to R
* VIDEOS:
    + Data camp: [Intro R lectures](https://www.datacamp.com/courses/free-introduction-to-r-beta) Chapters 1 (Intro to Basics), 2 (Vectors), 4 (Factors), and 5 (Data Frames)
    + Data camp: [R-markdown lectures]( https://www.datacamp.com/courses/reporting-with-r-markdown)
* READING:
    + Moore Ch. 1
    + Bailey Ch. 1
    + Grolemund & Wikham Ch. 27
    
* TASKS
    + Complete [tryGit](https://try.GitHub.io/levels/1/challenges/1)
    + Install git on your computer and push a test file to GitHub
    + Fill out Pre-course Survey [(Google Form)](https://goo.gl/forms/8cw5GZEyl1k3ynBY2)


```{r, echo = FALSE, results="asis"} 
# bib[90:97]
```

#### `r advdate(mon, 2)`: Introduction to R-Markdown, Managing Data, Replication, Git and GitHub

* VIDEOS:
    + Data camp: [Data minipulation lectures](https://www.datacamp.com/courses/dplyr-data-manipulation-r-tutorial)

* READING: 
    + Moore Chapter 5, 6
    + Bailey Chapter 2
    +
```{r, echo = FALSE, results="asis"} 
bib[author = "Dafoe"]
cat("\n    + ")
bib[author = "Eubank"]
cat("\n    + ")
bib["moravcsik_active_2010"]

```

#### `r advdate(mon, 3)`: Probability and Statistical Inference

* READING: 
    + Moore Chapter 9
    + Galimard Chapter 3 (photocopy)
```{r, echo = FALSE, results="asis"} 
#bib[author = "Dafoe"]
#cat("    + ")
#bib[author = "Eubank"]
```

#### `r advdate(mon, 4)`: Intro to graphics, Linear Regression Basics Review
* VIDEOS
    + Data camp: [ggplot lectures](https://www.datacamp.com/courses/data-visualization-with-ggplot2-1)
* READING:
    + Moore 2 (if you need algebra review)
    + Bailey Chapters 3, 4, 5
    + Fox Chapter 2
    + Grolemund Chapter 3
    +
```{r, echo = FALSE, results="asis"} 
bib["kastellec_using_2007"]
cat("\n    + ")
bib["king_making_2000"]
``` 

#### `r advdate(mon, 5)`: Data Transformation
* READING: 
    + Moore Chapter 3
    + Bailey Chapters 6.1-6.3, 7
    + Fox Chapters 4, 7.1-7.2
```{r, echo = FALSE, results="asis"} 

```

#### `r advdate(mon, 6)`: Interaction Terms, Simulation

* READING: 
    + Moore Chapter 7
    + Bailey 6.4
    + Fox 7.3
    +
```{r, echo = FALSE, results="asis"} 
bib[author = "Berry"]
cat("\n    + ")
bib[author = "Brambor"]
``` 

* **PAPER CHECK IN :  `r formatCourseDate(paperCheckIn)` **

####  `r advdate(mon, 7)`: Assumptions & Properties of Linear Regression 
* READING:
    + Bailey Ch. 14
    + Fox Ch.6 

#### `r advdate(mon, 9)` : LS and Causal Inference
- READING: 
    + TBD
    + TBD
- NO CLASS NOVEMBER 23, WORK ON YOUR PAPERS

#### `r advdate(mon, 8)`: Matrix Presentation of LS
* READING:  
    + Moore Chapter 12
    + Fox Chapter 9.1-9.2

#### `r advdate(mon, 10)`: Linear Regression Diagnostics and Fixes
- READING: 
    + Moore Chapter 12
    + Fox Chapter 9.1-9.2
    
#### `r advdate(mon, 11)`: Logit/Probit and Linear Probability Model
* READING: 
    + Bailey Ch. 12
    + Fox Ch. 14

####  `r advdate(mon, 12)`: Presentations 1


####  `r advdate(mon, 13)`: Presentations 2

<!-- ####  `r advdate(mon, 14)`: Presentations 3 OR Special Class on Text as Data
* TBD  -->

# Recommended Textbooks
There are many other important textbooks and at some point you may find yourself looking for a different explanation of something you didn't understand -- or looking to go deeper. Here are some places to start.

```{r, echo = FALSE, results="asis"}
bib[c("angrist_mostly_2008", "gailmard_statistical_2014", "gelman_data_2007", "greene_econometric_2003")]
```
